notes

### 2025-07-05 manuscript/notes/notes.Rmd
changes to notes.

@@

@@

>>>>

-> Done. I separated them before to avoid an almost blank page in the ms...

@@

-> Changed.

@@

-> This sentence has been removed. I added this sentence: "These minimal requirements are fulfilled by the RT data obtained in single-button detection tasks, where the time-to-response is repeatedly measured in different trials in the same individual. In section A of the Supplemental Material we visualize this and other types of time-to-event data which are typically obtained in discrimination and bistable perception tasks."
Thus, based on section A in the Supplemental Material, the distinction between single event and repeated events should be clear now.
